---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GradeCalculator

<!-- badges: start -->

<!-- badges: end -->

The goal of GradeCalculator is to give 'whatGrade()' which makes calculating the final exam grade you need to achieve a certain grade in a course easier.

## Installation

You can install the development version of GradeCalculator like so:

``` r
library(devtools)
install_github("stat545ubc-2022/assignment-b1-and-b2-asanaiman/GradeCalculator"))

# Once package is downloaded can load the package and use!
library(GradeCalculator)
```

## Example

This is a basic example which shows you how to solve a common problem:

There are 5 assignments in the course worth 10%, 20%, 5%, 30%, 5% prior to the final exam. Student received 70%, 80%, 100%, 60%, 60% respectively and they want a final grade of 78%.

***Note:*** *the weight of the assignments and the assignment grades need to be inputted in the same order.*

```{r example}
library(GradeCalculator)
whatGrade(c(10, 20, 5, 30, 5), c(70, 80, 100, 60, 60), 78) 
```
