---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gradecalculator

<!-- badges: start -->

<!-- badges: end -->

The goal of the **gradecalculator** package is to provide functions that allow students to calculate their course grades easily in different scenarios. For example, at what percent they currently stand in their course with the grades they have received thus far. This package currently only consists of one function, **'what_grade()'**. This function makes calculating the final exam grade you need to achieve a certain grade in a course easier.

## Installation

You can install the development version of gradecalculator like so:

``` r
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-asanaiman/gradecalculator"))
```

Once package is installed, to load the core gradecalculator and make it available in your current R session:

``` r
library(gradecalculator)
```

Now you can use the package!

## Example

This is a basic example which shows you how to use the gradecalculator package:

A student is taking a course. There are 5 assignments in the course worth 10%, 20%, 5%, 30%, 5% prior to the final exam. The student received 70%, 80%, 100%, 60%, 60% respectively on the assignments. The student wants a final grade of 75% in the course and want to calculate what grade they need on the final exam to achieve this.

| Assignment   | Weight of Assignment | Grade Received |
|--------------|----------------------|----------------|
| Assignment 1 | 10%                  | 70%            |
| Midterm 1    | 20%                  | 80%            |
| Quiz 1       | 5%                   | 100%           |
| Midterm 2    | 30%                  | 60%            |
| Quiz 2       | 5%                   | 60%            |

***Note:*** *the weight of the assignments and the assignments grade received need to be inputted in the same order.*

```{r example}
library(gradecalculator)
what_grade(c(10, 20, 5, 30, 5), c(70, 80, 100, 60, 60), 75) 
```
